Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-09-07 paper/current/main.tex

The axes can further be visualized to examine the relative position of organizations along the prestige axis, and along a geographic axis between California and Massachusetts to aid visualization.
Prestigious universities such as Columbia, Stanford, MIT, Harvard, and Rockefeller are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}c).
Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations for which rankings are often low-resolution or incomplete, such as regional and liberal arts universities, seminaries, musical schools, and community colleges (Fig.~\ref{fig:semaxis}d), or for which no such rankings exist, such as government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).

>>>>

The axes can further be visualized to examine the relative position of organizations along the prestige axis, and along a geographic axis between California and Massachusetts to aid visualization.
Prestigious universities such as Columbia, Stanford, MIT, Harvard, and Rockefeller are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}c).
Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations for which rankings are often low-resolution, incomplete, or entirely absent such as regional and liberal arts universities, seminaries, musical schools, and community colleges (Fig.~\ref{fig:semaxis}d), government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
Using SemAxis, we can even construct quantitative rankings for these types of organizations that correlate with their citation impact (Fig.~\ref{fig:supp:sector_semaxis_impact}.
